---
title: "Youtube video Analysis Cross Cultural"
author: "Ismayil"
date: "25 March 2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r global_options, include=FALSE, cache=FALSE}
library(knitr)
opts_chunk$set(echo=TRUE, 
               warning=FALSE, 
               message=FALSE,
               cache = TRUE,
               include = TRUE,
               results = 'show',
               error = TRUE)
```




## Loading the requires libraries

```{r}
library(rmarkdown)
library(rjson)
library(jsonlite)
library(pander)
library(cowplot)
library(tidyverse)
library(magrittr)
library(dplyr)
library(treemap)
library(scales)
library(ggplot2)
library(gplots)
library(tm)
library(SnowballC)
library(RSentiment)
library(data.table)
library(dplyr)
library(DT)
library(lubridate)
library(RColorBrewer)
library(plotrix)
library(corrplot)
library(ggdendro)
library(ggrepel)
library(wordcloud)
library(tidytext)
library(stringr)
library(tm)
library(sentimentr)
library(RSentiment)
```

## Loading the Data

```{r}

gbv = read.csv("MXvideos.csv")


```


# Reading and preparing data

```{r}

gb <- tail(fread("MXvideos.csv",encoding = "UTF-8"))
gb[,"Location":="MX"]



videos <- as.data.table(rbind(gb))
videos$trending_date <- ydm(videos$trending_date)
videos$publish_time <- ymd(substr(videos$publish_time,start = 1,stop = 10))
videos$dif_days <- videos$trending_date-videos$publish_time
```
## First lets see the CORRELATION

```{r}
corrplot(corr = cor(videos[,c("category_id","views","likes","dislikes","comment_count"),with=F]))
```

* We can see that between views and likes we have a high correlation, I thought that we will have a similar correlation between views and dislikes, but is almost half of the like correlation.

```{r}
gbv = gbv %>% mutate(category = case_when(
  category_id== '1' ~ 'Film and Animation',
  category_id== '2' ~ 'Autos and Vehicles',
  category_id== '10'~ 'Music',
  category_id== '15'~ 'Pets and Animals',
  category_id== '17'~ 'Sports',
  category_id== '18'~ 'Short Movies',
  category_id== '19'~ 'Travel and Events',
  category_id== '20'~'Gaming',
  category_id== '21'~'Videoblogging',
  category_id== '22'~ 'People and Blogs',
  category_id== '23'~ 'Comedy',
  category_id== '24'~ 'Entertainment',
  category_id== '25'~ 'News and Politics',
  category_id== '26'~ 'How to and Style',
  category_id== '27'~ 'Education',
  category_id== '28'~ 'Science and Technology',
  category_id== '29'~ 'Nonprofits & Activism',
  category_id== '30'~ 'Movies',
  category_id== '31'~ 'Anime/Animation',
  category_id== '32'~ 'Action/Adventure',
  category_id== '33'~ 'Classics',
  category_id== '34'~ 'Comedy',
  category_id== '35'~ 'Documentary',
  category_id== '36'~ 'Drama',
  category_id== '37'~ 'Family',
  category_id== '38'~ 'Foreign',
  category_id== '39'~ 'Horror',
  category_id== '40'~ 'Sci-Fi/Fantasy',
  category_id== '41'~ 'Thriller',
  category_id== '42'~ 'Shorts',
  category_id== '43'~ 'Shows',
  category_id== '44'~ 'Trailers'))
```

## Views per Category in Great Britian

```{r}
ggplot(gbv,aes(category,views))+geom_boxplot(fill = "black",color = "orange")+scale_y_log10()+
  theme(text = element_text(size=10),axis.text.x = element_text(angle=90, hjust=1))
```

## Top 10 popular Categories in Russia

```{r}
GB_Top10_Popular_Categories = gbv %>% count(category)%>% 
  arrange(desc(n))%>% head(10)%>%rename("No.of.Videos" = n)

ggplot(GB_Top10_Popular_Categories,aes(category,No.of.Videos))+
  geom_bar(stat = "identity",aes(fill=category))+theme(text = element_text(size=10),
                                                       axis.text.x = element_text(angle=90, hjust=1))
```






